Diffantom: a software layer to build digital phantoms of whole-brain diffusion MRI

### 2015-06-23 paper/main.tex
add licenses

\section*{Data Sharing}
{\color{red} Add here the pointers to data (dryad?) and software (github/zenodo doi) when available and say licences.}

>>>>

\section*{Data Sharing}
{\color{red} Add here the pointers to data (dryad?)}
Source code of \emph{diffantom} is available at \url{https://github.com/oesteban/phantomas} under an MIT licence.
\emph{Phantomas} is available in \url{https://github.com/ecaruyer/phantomas/} under the revised-BSD licence.
